	This project was really a great part of my life during the past half year. Because I had already completed most lab assignments of the second year courses, I had a lot of time to spare to work on the application. This resulted in many longs nights of debugging, refactoring and more debugging, most of the times along with one or more of my fellow group members. For me, this was basically a fun way to spend my time, because the group is one of the greatest groups I have ever worked with, and their dedication and motivation motivated me to return that favor, creating an in my opinion allround positive experience.\\

	The context of the project didn't invoke much of a reaction in me at first, mostly because I've never worked much in any area to do with Biology, but the title of the project and the idea of `Programing Life', actually influencing life by programming, did and still does sound quite cool. It's made me wonder about the possibilities that exist with the technoligies we have used and contributed to, and I think I would enjoy a career in Bioinformatics, even though it would never have guessed it would be one of my choices to begin with.\\

	One peculiar side effect that working on the project seemed to cause, was that I would find myself going to sleep with my head full of ideas on how to create new functionalities for the application or just ideas about cool software in general. This of course threw me into an upwards spiral of spending time working on the project, becoming more excited and as such spending even more time on the project. Overall I think this was a first for me, because usually in projects I get excited about it, but not this much.\\

	Another effect of the project was that suddenly everything even remotely related to bacterias or cells or products reminded me of our application, resulting in me showing and explaining what we had been working on recently to anybody fortunate enough to share in the conversation. All that explaining made me understand the context of the project better, making my interests in Biology and especially Bioinformatics grow.\\

	All in all, I have had a great time the past weeks, and I attribute that mostly the project. I learned a lot of new things and I had a lot of fun doing it, not to mention that in my opinion the end result was worth every bit of time put into it. I think it ultimately made me a better programmer and someone who is a little more informed on the inner workings of cells than most people.
